Understanding domestic abuse

### 2019-07-29 case_for_support_TM_hacked.tex
Anna cfs update

We will also explore the extent to which changes in alcohol consumption and financial stability on the community level affects the prevalence of domestic abuse. To do so, we will use the transaction data to construct an LSOA-level spending profile for a given time period to investigate how temporal changes in this profile affect the number of reported domestic abuse cases in that area, using a spatial panel regression model. This statistical estimation approach will alleviate the problem of spatial dependency between neighbourhoods, and will allow us to derive a precise estimate of the effect of temporal changes in community-level alcohol consumption and financial health on the prevalence of domestic abuse in the neighbourhood.

We will identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and  how these affect the reported number of domestic abuse incidents in that area in a given time period. Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won.

>>>>

We will also explore the extent to which changes in alcohol consumption and financial stability on the community level affects the prevalence of domestic abuse. To do so, we will use the transaction data to construct an LSOA-level spending profile for a given time period to investigate how temporal changes in this profile affect the number of reported domestic abuse cases in that area, using a spatial panel regression model. This statistical estimation approach will alleviate the problem of spatial dependency between neighbourhoods, and will allow us to derive a precise estimate of the effect of temporal changes in community-level alcohol consumption and financial health on the prevalence of domestic abuse in the neighbourhood. We will identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and explore how these affect the reported number of domestic abuse incidents in that area in a given time period. Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won.
